Trajipaq_sentiment_an

### 2023-08-12 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_an.Rmd
wtv

reg_WGI_can_2021_dico <- glm(formula = sentimapp_can_dico ~ wgi_origin_2021_score , data = trajipaq, family = "binomial") ## VD2 dichotomique
reg_WGI_can_2021_dico_ctrl <- glm(formula = sentimapp_can_dico ~ wgi_origin_2021_score  + age + education + sexe + origine + revenu + langue_mat + religion + statut_mat , data = trajipaq, family = "binomial")#VD2 contrôlée par CSD

@@

```{r}
stargazer(
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_long_ctrl,
  reg_WGI_can_arrival_long,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021_dico,
  reg_WGI_can_2021_dico_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_long_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021_dico,
  reg_WGI_can_2021_long_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_dico_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_long_ctrl,
  reg_WGI_can_2021_dico,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_long_ctrl,
  reg_WGI_can_2021_dico_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_long_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_long_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021_dico,
  reg_WGI_can_2021_dico_ctrl,
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_long_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

>>>>

reg_WGI_can_2021_dico <- glm(formula = sentimapp_can_dico ~ wgi_origin_2021_score , data = trajipaq, family = "binomial", na.action = na.pass) ## VD2 dichotomique
reg_WGI_can_2021_dico_ctrl <- glm(formula = sentimapp_can_dico ~ wgi_origin_2021_score  + age + education + sexe + origine + revenu + langue_mat + religion + statut_mat , data = trajipaq, family = "binomial")#VD2 contrôlée par CSD

@@

```{r}
stargazer(
  reg_WGI_can_2021_dico,
  reg_WGI_can_2021_dico_ctrl,
  reg_WGI_can_2021_long,
  title = "Results", 
  align = TRUE, 
  type = "text"
)
